plantecophys - an R package for analysing and modelling leaf gas exchange data

### 2015-10-06 manuscript.Rmd
Expanded description of FARAO

The `FARAO` function (FARquhar And Optimality) calculates optimal stomatal conductance based on the Cowan-Farquhar hypothesis. It finds the C~i~ for which the quantity $A - \lambda E$ is maximal, and then calculates corresponding A~n~ and g~s~, thus avoiding the specification of an f(D) function as in Eq. 4. This implementation was used by Medlyn et al. [@medlyn2011] to compare a simplified model of optimal stomatal conductance to the full numerical solution. In Fig. 4a, I have calculated $A - \lambda E$ across a range of C~i~ values, and for different values of D. The `FARAO` function calculates the optima of these curves, which can for example be used to study the response of stomatal conductance to D (Fig. 4b).

>>>>

The `FARAO` function (FARquhar And Optimality) calculates optimal stomatal conductance based on the Cowan-Farquhar [@cowan1977] hypothesis that stomata respond to environmental drivers in order to maximize photosynthesis while minimizing water loss. This implementation was used by Medlyn et al. [@medlyn2011] to compare a simplified model of optimal stomatal conductance to the full numerical solution.

To find optimal stomatal conductance, `FARAO` finds the C~i~ for which the quantity $A_n - \lambda E$ is maximal, where E is the leaf transpiration rate and $\lambda$ is the marginal cost of water (an empirical parameter related to g~1~, see [@medlyn2011]). A~n~ is calculated directly as a function of C~i~ via the FvCB model (Eq. 1), g~s~ is calculated by rearranging Eq. 3, and E is calculated assuming perfect coupling (thus $E = g_s D/P_a$, where P~a~ is atmospheric pressure). This numerical routine does not need specification of an f(D) function as in Eq. 4, instead, this function is an emergent property.  In Fig. 4a, I have calculated $A_n - \lambda E$ across a range of C~i~ values, and for different values of D. The `FARAO` function calculates the optima of these curves, which can for example be used to study the response of stomatal conductance to D (Fig. 4b).
